Efficient static analysis of Marlowe contracts

### 2020-05-28 papers/static_analysis2020/paper.tex
Tidied up bib and adsded orginal (ISoLA) Marlowe reference.

Thanks to static analysis, we can automatically check beforehand whether any
payments promised by a Marlowe contract can be fulfilled in every
possible execution of the contract. If a Marlowe contract has passed
the static analysis, we will have a very high assurance
that whenever the contract says it will make a payment, the contract will
indeed have enough money available.

@@

Firstly, we introduce the semantics of Marlowe, the guarantees
that are offered implicitly by the semantics, and how the design choices
facilitate static analysis and make it decidable. A more detailed
explanation can be found in \cite{marlowe}.

>>>>

Thanks to static analysis, we can automatically check beforehand whether any
payments promised by a Marlowe~\cite{Marlowe:2018,marlowe} contract can be fulfilled in every
possible execution of the contract. If a Marlowe contract has passed
the static analysis, we will have a very high assurance
that whenever the contract says it will make a payment, the contract will
indeed have enough money available.

@@

Firstly, we introduce the semantics of Marlowe, the guarantees
that are offered implicitly by the semantics, and how the design choices
facilitate static analysis and make it decidable. A more detailed
explanation can be found in \cite{marlowe2020}.
